Lineage Metrics Analysis

### 2018-03-28 analysis/data_analysis.Rmd
Make figure size reasonable

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=max_pairwise_distance, color=mutation_rate)) + facet_wrap(~problem, ncol=8, scales="free") + theme_classic()
```

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=dominant_deleterious_steps, color=mutation_rate)) + facet_wrap(~problem, ncol=8, scales="free") + theme_classic()
ggsave("../figs/dom_deleterious_mutation_rate.png")
```

@@

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=variance_deleterious_steps, color=mutation_rate)) + facet_wrap(~problem, ncol=8, scales="free") + theme_classic()
ggsave("../figs/variance_deleterious_mutation_rate.png")
```

>>>>

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=max_pairwise_distance, color=mutation_rate)) + facet_wrap(~problem, scales="free") + theme_classic()
```

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=dominant_deleterious_steps, color=mutation_rate)) + facet_wrap(~problem, scales="free") + theme_classic()
ggsave("../figs/dom_deleterious_mutation_rate.png", width = 3.5)
```

@@

```{r, echo=FALSE}
ggplot(subset(tournament_data, tournament_data$update==5000 & tournament_data$ts == 4)) + geom_boxplot(aes(x=mutation_rate, y=variance_deleterious_steps, color=mutation_rate)) + facet_wrap(~problem, scales="free") + theme_classic()
ggsave("../figs/variance_deleterious_mutation_rate.png", width = 3.5)
```
